Quality measure notes

### 2021-05-30 StateOfPractice/Ao-Report/13Methods.tex
ao's report - minor updates

\subsection{Interview Methods}
Before contacting any interviewee candidate, the study had been reviewed by the McMaster University Research Ethics Board and received ethics clearance.

>>>>

\subsection{Interview Process}
Before contacting any interviewee candidate, the study had been reviewed by the McMaster University Research Ethics Board and received ethics clearance.
